The Astropy Project

### 2017-11-10 main.tex
remove duplication

As detailed in APE 2 \citep{ape2}, the \astropypkg release schedule

@@

\begin{description}
    \item[Speed improvements] \inlinecomment{TODO}{Marten}
    \item[Logarithmic units and magnitudes] By default, taking the logarithm of
        a \texttt{Quantity} object with non-dimensionless units intentionally
        fails.
        However, some well-known units are actually logarithmic quantities,
        where the logarithm of the value is taken with respect to some reference
        value.
        Examples include astronomical magnitudes, which are logarithmic fluxes,
        and decibels, which are more generic logarithmic ratios of quantities.
        Logarithmic, relative units are now supported in \texttt{astropy.units}.
    \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see
        \sectionname~\ref{sec:table}) now supports using quantities in tables
        with the \texttt{QTable} class.
        As a result, units specified in FITS tables are supported, and tables
        with quantities can be read and written to various file formats.
    \item[Defining functions that require quantities] When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        These requirements often lead to implementing repetitive code for
        validating \texttt{Quantity} inputs.
        \texttt{astropy.units} now provides a \python decorator
        (\texttt{quantity_input}) that does this verification automatically.
    \item[Interaction with \package{numpy} arrays] \inlinecomment{TODO}{Marten}
\end{description}

>>>>

@@

\begin{description}
    \item[Speed improvements] \inlinecomment{TODO}{Marten}
    \item[Logarithmic units and magnitudes] By default, taking the logarithm of
        a \texttt{Quantity} object with non-dimensionless units intentionally
        fails.
        However, some well-known units are actually logarithmic quantities,
        where the logarithm of the value is taken with respect to some reference
        value.
        Examples include astronomical magnitudes, which are logarithmic fluxes,
        and decibels, which are more generic logarithmic ratios of quantities.
        Logarithmic, relative units are now supported in \texttt{astropy.units}.
    \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see
        \sectionname~\ref{sec:table}) now supports using quantities in tables
        with the \texttt{QTable} class.
        As a result, units specified in FITS tables are supported, and tables
        with quantities can be read and written to various file formats.
    \item[Defining functions that require quantities] When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        These requirements often lead to implementing repetitive code for
        validating \texttt{Quantity} inputs.
        \texttt{astropy.units} now provides a \python decorator
        (\texttt{quantity\_input}) that does this verification automatically.
    \item[Interaction with \package{numpy} arrays] \inlinecomment{TODO}{Marten}
\end{description}
